---
title: "Lompoc WRP Analysis"
author: "Taylor Medina"
date: "12/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(janitor)
library(kableExtra)
```

**Concentration Difference:** $\Delta$ [PFA] = Effluent - Influent

- A positive concentration difference means that there is a greater concentration in the effluent than the influent

```{r}
lompoc <- read_csv("lompoc.csv") %>% 
  clean_names() %>% 
  filter(field_pt_name %in% c("EFF-001", "INF-001"),
         units == "NG/L",
         parvq == "=") %>% 
  mutate(field_pt_name = case_when(
    field_pt_name == "EFF-001" ~ "EFFLUENT",
    field_pt_name == "INF-001" ~ "INFLUENT")) %>% 
  unite("parameter", parameter:parameter_name, sep = " ")
```

```{r}
lompoc_summary <- lompoc %>% 
  group_by(parameter, field_pt_name, samp_date) %>% 
  summarize(mean_conc  = mean(value, na.rm = TRUE)) %>% 
  pivot_wider(names_from = field_pt_name,
              values_from = mean_conc)

lompoc_summary[is.na(lompoc_summary)] <- 0

lompoc_1 <- lompoc_summary %>%
  filter(samp_date == "3/9/2021") %>% 
  mutate(difference = EFFLUENT - INFLUENT) %>% 
  filter(difference > 2)

lompoc_2 <- lompoc_summary %>%
  filter(samp_date == "6/17/2021") %>% 
  mutate(difference = EFFLUENT - INFLUENT) %>% 
  filter(difference > 2)
```
### Significant PFA concentration differences
```{r}
ggplot(data = lompoc_1,
       aes(x = parameter, y = difference)) +
  geom_bar(stat = "identity", width = 0.5) +
  geom_hline(yintercept = 0) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  labs(x = "PFA",
       y = "Concentration difference (ng/L)",
       title = "3/9/2021") +
  theme_classic()

ggplot(data = lompoc_2,
       aes(x = parameter, y = difference)) +
  geom_bar(stat = "identity", width = 0.5) +
  geom_hline(yintercept = 0) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10),
                   guide = guide_axis(n.dodge = 2)) +
  labs(x = "PFA",
       y = "Concentration difference (ng/L)",
       title = "6/17/2021") +
  theme_classic()
```

### Concentration Difference Summary Table
```{r}
total_lompoc <- rbind(lompoc_1, lompoc_2) %>% 
  select(parameter, samp_date, difference) %>% 
  pivot_wider(names_from = parameter,
              values_from = difference)

total_lompoc %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

**Data:** Stevens, Brian (2021). Laboratory Analytical Reports (EDF) for the Lompoc City Regional Wastewater Reclamation Plant (NPD100051494). Retrieved from: https://geotracker.waterboards.ca.gov/profile_report?global_id=NPD100051494

